---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  overwrite = TRUE,
  fields = list(
    Title = "Explore dependencies pitfalls",
    Description = "Test behavior of the different types of depencies with local and CI check",
    `Authors@R` = c(
      person(given = "Swann", family = "Floc'hlay", email = "swann@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0003-1477-830X")),
      person("ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license()
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local(force = TRUE)
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("swann@thinkr.fr")
# NEWS
usethis::use_news_md()
```

```{r}
# ignore project file
usethis::use_git_ignore("*.Rproj")
```


**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
usethis::create_github_token()
gitcreds::gitcreds_set()

# _All-in-one share of your package and its documentation on GitHub
fusen::init_share_on_github()

# _Or one step at a time
# Send your project to a new GitHub project (included in `init_share_on_github()`)
usethis::use_github(
  organisation = NULL,
  private = TRUE)

# Set Continuous Integration
# _GitHub (included in `init_share_on_github()`)
usethis::use_github_action_check_standard()
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
# _GitLab
# gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown")
```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check()
checkhelper::check_as_cran()

# Add a new flat template
fusen::add_flat_template("add")
fusen::add_additional(flat_name = "regress_dataset")
```

# Share the package

```{r}
# set and try pkgdown documentation website locally
usethis::use_pkgdown()
pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)

# Share your package and its documentation on GitHub
# usethis::create_github_token()
# gitcreds::gitcreds_set()
fusen::init_share_on_github()
```

